Anomalous waves triggered by abrupt depth changes: experiments and truncated KdV theory

### 2019-10-09 paper2_JNLS/paper.tex
NM

	We note that the experiments discussed here preceded the development of the theory, and hence had no intent of mimicking a Gibbs measure, such as that in \eqref{Gibbs}. We expect that if the driving featured in the experiments were designed to mimic the Gibbs measure, in particular the spectral decay, then it would be more straightforward to assign a value to the model parameter $\lamfac$. We, however, leave that task for future research due to the significant cost of performing an entirely new set of experiments compared to the relative ease and great value in re-analyzing existing experimental measurements in light of the new theoretical developments.

@@

	We now aim to compare the statistics measured in the experiments versus the theory. We focus on the representative set of experiments detailed in Table \ref{paramtable}. In these experiments, the peak downstream skewness measured was 0.83. We can then use Fig.~\ref{transfig}(c) as a guide to select the upstream inverse temperature $\thup$. With $(\Lambda, \lamfac) = (16, 8)$ fixed, the figure indicates a value of $\thup = 17$ to achieve the desired skewness. We thus run the DNS with these model parameters (and with a sufficiently fine timestep, and number of samples, and to a final dimensionless time of 10).

	Figure \ref{uhist} shows displacement histograms from these TKdV simulations in comparison to the experiment histograms. The later representative exactly the same data as shown in Fig.~\ref{ExpDiagStats}, only converted to the dimensionless variables. The TKdV simulations do a remarkable job of capturing both the symmetric upstream statistics and the skewed downstream statistics. Amazingly, the simulations reproduce the measured distributions in great detail, both in the shape of the distribution and the scale.
%
This comparison offers convincing evidence that the theory works and the parameters have been matched as well as possible.

@@

>>>>

	We note that the experiments discussed here preceded the development of the theory, and hence had no intent of mimicking a Gibbs measure in the wave forcing. We expect that if this forcing were designed to mimic the Gibbs measure, in particular the spectral decay, then it would be more straightforward to assign a value to the model parameter $\lamfac$. We, however, leave that task for future research due to the significant cost of performing an entirely new set of experiments compared to the relative ease and great value in re-analyzing existing experimental measurements in light of the new theoretical developments.

@@

	We now aim to compare the statistics measured in the experiments versus the theory. We focus on the representative set of experiments detailed in Table \ref{paramtable}. In these experiments, the peak downstream skewness is measured to be $\max \skw(\uup) = 0.83$. We can then use Fig.~\ref{transfig}(c) as a guide to select the upstream inverse temperature $\thup$. With $(\Lambda, \lamfac) = (16, 8)$ fixed, the figure indicates a value of $\thup = 17$ to achieve the desired skewness. We thus run the DNS with these model parameters (and with a sufficiently fine timestep, and number of samples, and to a final dimensionless time of 10).

	Figure \ref{uhist} shows displacement histograms from these TKdV simulations in comparison to the experiment histograms. The later representative exactly the same data as shown in Fig.~\ref{ExpDiagStats}, only converted to the dimensionless variables. The TKdV simulations do a remarkable job of capturing both the symmetric upstream statistics and the skewed downstream statistics. Amazingly, the simulations reproduce the measured distributions in great detail, both in the shape of the distribution and the scale.
%
This comparison offers convincing evidence that the theory works and the parameters have been matched as well as possible. \nick{Reword}

@@

	These slope histograms show intriguing similarities and differences. First, the upstream slope distribution is captured well by the TKdV simulations, both in its nearly symmetric shape and its scale. We note that, while the standard deviation of displacement was input into the TKdV theory, the slope standard deviation was not. Downstream, both the experimental and theoretical slope distributions  spread significantly. Interestingly, in the experiments, it is not the standard deviation of slope that increases significantly upon crossing the depth change ($\std(\eta_x)$ increases from 0.15 to 0.17), but the excess kurtosis, which jumps from a value of 0.46 to 3.4. Likewise, in the TKdV theory, $\std(\eta_x)$ grows from 0.13 upstream to 0.33 downstream, and $\kurt(\eta_x)$ grows from -0.04 to 0.50. Thus, the jump in kurtosis, while not as extreme as that measured in experiments, is quite significant in the theory. These elevated levels of kurtosis give the distributions the look of being stretched in the tails and pointy near the centers (especially in the experiments).

	Distinct differences in the shapes of the downstream slope distributions, however, are visible. While the theoretical distributions remain symmetric, the experimental distributions skew towards negative slope. As mentioned earlier, this skewness is consistent with a right-moving wave of steep leading surface (i.e.~negative slope), which is a phenomenon apparently not captured by the TKdV simulations.
Finally, it should be commented that the experimental measurements of slope involve numerical differentiation of the free surface extracted from optical images, which naturally introduces error. Furthermore, high-order statistics, such as kurtosis, can be very sensitive to noise and measurement error. Hence, the experimental statistics of slope, while they are valuable, should be regarded with some level of caution.
